\documentclass[a4paper,12pt]{article}
\usepackage[T2A]{fontenc}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[breakable]{tcolorbox}
\usepackage{booktabs}
\usepackage{array}
\usepackage{paralist}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{pifont}
\usepackage{subfig}
\usepackage{indentfirst}
\usepackage{tocbibind}
\usepackage{grffile}
\usepackage{parskip}
\usepackage{caption}
\usepackage{float}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{calc}
\usepackage{epstopdf}

\title{Collection, analysis and predictive analytics of open data sources}
\author{}
\date{\today{}}

\begin{document}

\maketitle{}

\section{Project goals}
The project itself represents a multipage interactive dashboard with plots related to the most common topics in macroeconomics: gross domestic product, national income, trading indicators, inflation, demography, social-related data and much more.
Moreover, the project includes configurable machine learning modules for making macroeconomics research more functional and accessible.
Sometimes macroeconomics data visualized in plots seems to be either too complicated to understand or hard to interpret due to poor visualization practices.

The project goal is to solve this problem by providing macroeconomics researchers with both high-quality and user-friendly visualizations.
In other words, the project is designed to help macroeconomics researchers generate ideas or hypotheses for deep analysis of the different aspects of macroeconomics.
Furthermore, in order to improve the research experience, the most cutting-edge technologies were used for time series forecasting, feature-based country clustering and an agentic system included in the dashboard.

Most data used in the dashboard is from \href{https://data360.worldbank.org/en/search}{World Bank Data API}. Nevertheless, in order to introduce a more complex outlook on the macroeconomic situation, other data sources are included as well: news articles parsed from the open \href{https://github.com/Webhose/free-news-datasets}{Webz.io News Dataset Repository} that is used for local RAG and improved fact-based inference of the agentic system.
In addition, as global macroeconomics is significantly affected by financial markets, data from \href{https://finance.yahoo.com/}{Yahoo Finance} is utilized as well.

To sum up, the general purpose of the project is to create a highly technological, complex intellectual system for improving the research experience of macroeconomists.

\section{Project Overview}
As mentioned before, the project includes plenty of various visualizations of main macroeconomic (and other) indicators, separated by pages.
Each page is dedicated to a specific sub-topic: "General Economics indicators", "Economy Structure", "Finance and Monetary" etc.
On each page of the dashboard there are three main types of plots for each presented indicator: a map with visualization of the indicator across countries, the dynamics of the indicator over time for selected countries, and the distribution of the indicator across countries in the selected year.
Each of these plots is highly configurable: the user can apply a log-transformation to it, filter by years or countries and even create a brief overview of the graph using an LLM.

Moreover, on some pages of the dashboard custom plots are introduced --- this is an option left for the project's extensibility in terms of shown visualizations.
Additionally, other pages of the dashboard include graphs built using other data sources, along with the opportunity to set up a custom plot, configure and run clustering, and discuss the dashboard with an AI Agent which has full access to the macroeconomics data and has a low risk of hallucinations.

\section{Architecture and technical stack of the project}
During the development of the project a modern and reliable tech stack was used. For the relational database \href{https://www.postgresql.org/}{PostgreSQL} was used, while for vector storage \href{https://qdrant.tech/}{Qdrant} was utilized.
For secure deployment \href{https://nginx.org/}{NGINX} was used.
The application relies on the micro-service architectural style via multiple \href{https://www.docker.com/}{Docker} containers.
Most of the code is written in \href{https://www.python.org/}{Python} with the most popular frameworks for specific tasks: \href{https://streamlit.io/}{Streamlit}, \href{https://plotly.com/}{Plotly}, \href{https://pola.rs/}{Polars}, \href{https://pydantic.dev/}{Pydantic}, \href{https://fastapi.tiangolo.com/}{FastAPI}, \href{https://docs.langchain.com/oss/python/langgraph/overview}{LangGraph}

\section{Project result}
Final and temporary versions of the dashboard can be accessed at the \href{https://github.com/alexveider1/Ultimate-Macroeconomics-Dashboard}{GitHub Repository}.
Repository includes two branches: "main" for local usage and "hosting" for deployment.
More information and detailed installation guides for both use-cases can be found in the "README.md" file in the repository.

\newpage{}

\tableofcontents{}

\end{document}
